### 2014-09-11 LaTeX/RhodiumTheory.tex
Added to theory section (incomplete)

We suspect that substate factors will determine the economic impacts of civil conflict.  In particular, citizens must be able and willing to participate in commerce.  When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.  Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.  For this same reason, violence near important transporation hubs such as airports and sea ports should threaten business.

While this hypothesis may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.  While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.  Conflict area is only one possible proxy for overall destructiveness.  However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) those resources outlined above.  In fact, we feel measures of proximity rather than spread are more appropriate to test the hypothesis that conflict obstucts vital economic activity.

@@

We turn now to an empirical test of our proposition.  Using a dataset that includes 510 instances of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.

>>>>

We suspect that substate factors will determine the economic impacts of civil conflict.  In particular, citizens must be able and willing to participate in commerce.  When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.  Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.

While this hypothesis may resemble those of \cite{imai:weinstein:2000}, ours differs in the hypothesized mechanism through which conflict affects economic performance.  While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.  Conflict area is only one possible proxy for overall destructiveness.  However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) the urban centers described above.  In fact, we anticipate measures of proximity rather than spread to be more appropriate to test the hypothesis that conflict obstructs vital economic activity.

\cite{glaeser:shapiro:2001} discuss the historic role of cities in warfare and their current role with respect to terrorism. Cities, they argue, once provided safe haven in the midst of conflict; defense of a concentrated population is easier than defense of a dispersed population. However, as the tactics of warfare have shifted over the centuries, the relationship between violent conflict and cities has become more complex. Their dense populations also tempt belligerents and maximize the impact to cost ratio of a given violent action. Finally, the authors point out that warfare destroys transportation infrastructure which can interfere both with commerce and with rebuilding during a conflict.

That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies. \cite[p. 137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the national state in economic analysis \citep{jacobs:1969,jacobs:1984}.  In the past three decades, economists have begun

@@

We turn now to an empirical test of our proposition.  Using a dataset that includes 510 years of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
